Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-27 paper.tex
rephrased lemma 2 and lemma 4

\begin{lemma}
Define $\tau$ to be any random variable that is almost surely between $t_n$ and $t_{n+1}-1$, we have 
\begin{align}
P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right), \nonumber
\end{align}
for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

@@

\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
Let $X_{i}$ be zero mean $1/2$-subgaussian random variables. $\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk. Let $J$ be any random variable taking values in $\mathbb{N}$. If
\begin{align}
f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
\end{align}
then
\begin{align}
Pr[S_{J}\geq f(J)]\leq 12e^{-1.8b}. \nonumber
\end{align}
\label{ACI-inequality}
\end{lemma}

>>>>

\begin{lemma}
Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filteration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have 
\begin{align}
P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right), \nonumber
\end{align}
for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

@@

\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
Let $X_{i}$ be zero mean $1/2$-subgaussian random variables. $\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk. Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$. We let $J$ take a special value $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$. If
\begin{align}
f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
\end{align}
then
\begin{align}
Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
\end{align}
\label{ACI-inequality}
\end{lemma}
